BAI resiliences ten droughts

### 2018-02-14 analysis/bai/trends_resilience_bai.Rmd
organizar estos

>>>>

!!!!!!!! ----- ESTO QUE esl lo que es!!!! compaeeee 
# With error bar 
sdfbe <- s %>% filter(samps >= 10) %>% group_by(disturb_year) %>% 
  summarise_at(c("rt_mean", "rs_mean", "rc_mean", "rrs_mean"), funs(mean(., na.rm = TRUE), sd(., na.rm=TRUE),se=sd(., na.rm=TRUE)/sqrt(n()))) %>% 
  inner_join(dy, by=c("disturb_year" = "maxyear"))
